Presentation Title

### 2017-08-14 paper/s1-intro.tex
Improve abstract
Update code URL in README

Recent research has developed a class of hybrid systems which uses PoW for committee election,
and Byzantine consensus algorithms to agree on transactions, e.g. SCP~\cite{luu2015scp}, ByzCoin~\cite{kogias2016enhancing} and Solidus~\cite{abraham2016solidus}.
This design is primarily for permissionless system because the PoW leader election aspect prevents Sybils.
This technique overcomes the early blockchain scalability issue by delegating the transaction validation to the Byzantine consensus protocol (e.g. PBFT in ByzCoin~\cite{kogias2016enhancing}).
A major tradeoff of such systems is that they cannot guarantee correctness when there is a large number of malicious nodes (but less than a majority).
For SCP, ByzCoin and Solidus, they all have some probability to elect more than $t$ Byzantine nodes into the committee,
where $t$ is typically just under a third of the committee size (a lower bound of Byzantine consensus~\cite{pease1980reaching}).
This problem is especially difficult to solve because the committee is always much smaller than the population size which has more than $t$ Byzantine nodes.
Again, due to the fact that these systems must reach consensus on all transactions,
none of them achieves horizontal scalability.

@@

% research question
In this work, answer the following research question.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault-tolerant and horizontally scalable?}
\end{displayquote}
A blockchain consensus protocol should be application neutral,
for example PoW without the transaction logic.
Our system should be Byzantine fault tolerant up to some threshold.
The threshold may be made adjustable by trading off performance.
Finally, we are interested in horizontal scalability in the general case, as it enables ubiquitous use.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.

% contribution
The key insight is to \emph{not} reach consensus using an existing consensus algorithm (a modified HoneyBadgerBFT~\cite{miller2016honey}) on transactions themselves but on special blocks called checkpoint blocks,
such that transactions are nevertheless verifiable at a later stage by any node in the network.
Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---\textsc{Checo}\footnote{\emph{Che}ckpoint \emph{co}nsensus}.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontally scalable for the first time.
    \item We analyse \textsc{Checo} to ensure correctness as defined in our architecture.
    \item We provide an implementation and then experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

>>>>

Recent research has developed a class of hybrid systems which uses PoW for committee election,
and Byzantine consensus algorithms to agree on transactions, e.g. SCP~\cite{luu2015scp}, ByzCoin~\cite{kogias2016enhancing} and Solidus~\cite{abraham2016solidus}.
This design is primarily for permissionless system because the PoW leader election aspect prevents Sybils.
This technique overcomes the early blockchain scalability issue by delegating the transaction validation to the Byzantine consensus protocol (e.g. PBFT in ByzCoin~\cite{kogias2016enhancing}).
A major tradeoff of such systems is that they cannot guarantee correctness when there is a large number of malicious nodes (but less than a majority).
For SCP, ByzCoin and Solidus, they all have some probability to elect more than $t$ Byzantine nodes into the committee,
where $t$ is typically just under a third of the committee size (a lower bound of Byzantine consensus~\cite{pease1980reaching}).
This problem is especially difficult to solve because the committee is always much smaller than the population size which has more than $t$ Byzantine nodes.
Again, due to the fact that these systems must reach consensus on all transactions,
none of them achieves horizontal scalability.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.

@@

% research question
Thus far, there are no systems that achieve horizontal scalability in the general case.
In this work, answer the following research question.
\begin{displayquote}
\emph{Is it possible to design a blockchain consensus protocol that is fault-tolerant and horizontally scalable?}
\end{displayquote}
A blockchain consensus protocol should be application neutral,
for example PoW without the transaction logic.
Our system should be Byzantine fault tolerant up to some threshold.
The threshold may be made adjustable by trading off performance.
Finally, we are interested in horizontal scalability in the general case, as it enables ubiquitous use.

% contribution
The key insight is to \emph{not} reach consensus using an existing consensus algorithm (a modified HoneyBadgerBFT~\cite{miller2016honey}) on transactions themselves but on special blocks called checkpoint blocks,
such that transactions are nevertheless verifiable at a later stage by any node in the network.
Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---\textsc{Checo}\footnote{Derived from ``\emph{Che}ckpoint \emph{co}nsensus''.}.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontally scalable in the general case for the first time.
    \item We analyse \textsc{Checo} to ensure correctness as defined in our architecture.
    \item We provide an implementation and then experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}
